\documentclass[10pt]{article}

% -- packages --
\usepackage{multicol}
\usepackage{amssymb}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{multirow}
\usepackage{bm}
\usepackage{array}
\usepackage{amsmath,latexsym}
\usepackage{csquotes}
\usepackage{verbatim}
\usepackage{tipa}
\usepackage{enumitem}
\usepackage[pdftex]{graphicx}
\usepackage{xparse}

% -- formatting --
\pagestyle{empty}
\geometry{left=0.65in, right=0.57in, top=0.70in, bottom=0.5in}
\renewcommand*\familydefault{\sfdefault}
\setlength{\parindent}{-2mm}
\setlength{\tabcolsep}{5pt}
\setitemize[0]{leftmargin=0.4cm, itemsep=0.1cm}

% -- new list definition -- # very useful!
\newlist{myitemize}{itemize}{2}
\setlist[myitemize,1]{label=$\bullet$,leftmargin=4mm,topsep=2mm,itemsep=2mm,itemindent=0mm,parsep=-0.5mm}
\setlist[myitemize,2]{label=$\circ$,leftmargin=4mm,topsep=1mm,itemsep=1mm,itemindent=0mm,parsep=-0.5mm}
%\setlist[myitemize,1]{label=$\bullet$}
%\setlist[myitemize,2]{label=$\circ$}

% -- color definitions --
\definecolor{llb}{rgb}{0.35,0.35,0.35}
\definecolor{bl}{RGB}{173,216,230}

% -- new commands --
\newcommand{\highlight}[1]{\framecolorbox[\textwidth]{black}{bl}{\makebox[\textwidth][l]{\bfseries \color{black} #1}}}
\newcommand{\mystyle}[1]{\textit{\textit{\textcolor{llb}{#1}}}}
\newcommand{\guide}[1]{\textit{\textit{\textcolor{llb}{#1}}}}
\NewDocumentCommand{\framecolorbox}{oommm}{
% #1 = width (optional)
% #2 = inner alignment (optional)
% #3 = frame color
% #4 = background color
% #5 = text
\IfValueTF{#1}
{\IfValueTF{#2}{\fcolorbox{#3}{#4}{\makebox[#1][#2]{#5}}}{\fcolorbox{#3}{#4}{\makebox[#1]{#5}}}}
{\fcolorbox{#3}{#4}{#5}}
}

% -- document begins here --
\begin{document}
%\fontfamily{lmr}
%\fontfamily{qcs}
%\fontfamily{cmss}
%\fontfamily{phv}

	% -- for grades --
	\vspace*{155pt}
	%\vspace*{124pt}

	\highlight{RELEVANT COURSES}\\[0.08cm]
	\begin{tabular}{ l l l l }
		\textbullet\ Computer Networks &  \textbullet\ Wireless Communication & \textbullet\ Machine Learning & \textbullet\ Digital Signal Processing
	\end{tabular}
	\setlength{\tabcolsep}{0.2cm}
	
	\highlight{SCHOLASTIC ACHIEVEMENTS}
	\begin{myitemize}[leftmargin=0.4cm]
		\item \textbf{99.68} percentile in \textbf{GATE} in Electronics and Communication among \textbf{1,52,318} candidates \hfill{(\textit{2016})}\\[-0.6cm]
		\item Secured an all India rank of \textbf{7578} in \textbf{AIEEE} \hfill{(\textit{2012})}\\[-0.6cm]
		\item \bm{$3^{rd}$} runner up in \textbf{national level} abacus competition by SIP-INDIA \hfill{(\textit{2008})}
	\end{myitemize}

	\highlight{MAJOR PROJECTS AND SEMINAR}
	\begin{myitemize}[leftmargin=0.4cm]
	\item \textbf{M.Tech Project: OpenFlow Router with eBPF Forwarding Engine}
	\hfill{(\textit{May'19 - Present})} \\
	\guide{Guide: Prof. D. Manjunath, IIT Bombay}\\
	\textbf{Objective:} Create a fast data plane forwarding device for small to medium networks.\\
	\textbf{Completed work:} Put together the functional requirements of controller and switch.\\
	\textbf{Ongoing \& future work:}
		\begin{myitemize}
			\item Using POX controller to communicate with OpenVSwitch via \textbf{OpenFlow} protocol.
			\item Using \textbf{eBPF in kernel space} as backend for fast packet forwarding, and less number of packet copies.
			\item Implementing a level-compressed \textbf{TRIE} for fast lookup.
			\item Porting the entire system to a \textbf{SPARC processor} on FPGA, as a prototype for IoT deployment.
			\item Benchmark testing of the system.
		\end{myitemize}

	\item \textbf{Seminar: Open Source Router}
	\hfill{(\textit{Jul'18 - Dec'18})}\\
	\guide{Guide: Prof. D. Manjunath, IIT Bombay}
		\begin{myitemize}
			\item \textbf{Studied} Click Modular Router, Extended Berkely Packet Filter, Network Processor Architecture and Software Defined Networking (SDN).
			\item \textbf{Implemented} a basic version of Click modular router, to work as an Ethernet switch.
		\end{myitemize}

	\end{myitemize}

	\highlight{WORK EXPERIENCE}
	\begin{myitemize}
		\item \textbf{Software Developer} \textpipe\ \mystyle{Nykaa} \hfill{(\textit{Jun'16 - Jul'17})}
		\begin{myitemize}
			\item \textbf{Responsibilities:} Involved in \textbf{development} of product listing, search, and checkout domains of the website.
			\item Closely worked with marketing team to strategically place tracking tags at numerous locations of the website.
			\item \textbf{Softwares used:} HTML, Javascript, jQuery, Magento Framework, PHP
		\end{myitemize}

		\item \textbf{Teaching Assistant: Communication Networks} \textpipe\ \mystyle{IIT Bombay, IIT Dharwad} \hfill{(\textit{Jan'19 - Apr'19})}\\
		\guide{Instructor: Prof. D. Manjunath, IIT Bombay}
		\begin{myitemize}
			\item \textbf{Created} and evaluated \textbf{7} lab experiments based on \textbf{socket programming}.
			\item Work also involved \textbf{traveling}, setting up lab experiments and evaluations at \textbf{IIT Dharwad}.
		\end{myitemize}

		\item \textbf{System Administrator} \textpipe\ \mystyle{Electrical Department, IIT Bombay} \hfill{(\textit{Jul'17 - Present})}
		\begin{myitemize}
			\item \textbf{Development} of EE department website, Dashboard, and maintaining numerous portals like faculty search committee, meeting room booking system, faculty wiki pages, and TA allotment portals.
			\item Provide mail service, storage space, computing, and network facilities to the Department.
			\item \textbf{Automation} of admission process through web-based services and \textbf{Bash Scripts.}
		\end{myitemize}
	\end{myitemize}

	\highlight{KEY COURSE PROJECTS AND SEMINAR}
	\begin{myitemize}
		\item \textbf{Simulation of Cellular system in MATLAB}
		\hfill{(\textit{Jan'18 - Apr'18})}\\
		\guide{Instructor: Prof. Abhay Karandikar, IIT Bombay}
		\begin{myitemize}
			\item Computed \textbf{SIR, blocking probability} for different cluster sizes and \textbf{sectoring}. Analyzed \textbf{handover} process and \textbf{ping-pong} rate for different user mobilities and hysteresis values.
			\item Analyzed BER performance for \textbf{space and time diversity} in a slow, flat fading Rayleigh channel.
			\item Analyzed BER performance for a \textbf{single-cell} and \textbf{multi-cell} scenario in a \textbf{CDMA} cellular system.
		\end{myitemize}
\newpage
		\item \textbf{Different Scheduling Schemes in LTE}
		\hfill{(\textit{Jan'18 - Apr'18})}\\
		\guide{Instructor: Prof. Abhay Karandikar, IIT Bombay}
		\begin{myitemize}
			\item Simulated channel aware schemes: Maximum Throughput \textbf{(MT)}, Proportional Fair \textbf{(PF)}, Throughput to Average \textbf{(TTA)} scheduling schemes in \textbf{LTE} Downlink.
			\item Used Cell Throughput, Average user throughput, and Jain Fairness Index as metrics for comparision.
		\end{myitemize}

		\item \textbf{Basic Image Editor}
		\hfill{(\textit{Jul'18 - Nov'18})}\\
		\guide{Instructor: Prof. Amit Sethi, IIT Bombay}
		\begin{myitemize}
			\item \textbf{Developed} a web-based, cross-platform GUI to perform operations on images.
			\item Showcased Histogram Equalization, Log transform, Gamma Correction, Blurring, Sharpening, Median filtering techniques in the application.
			\item Implemented full inverse filtering, truncated inverse, approximate wiener, and constrained least square filtering to \textbf{deblur} the input image.
		\end{myitemize}

		\item \textbf{Image Dehazing through Depth estimation}
		\hfill{(\textit{Jul'18 - Nov'18})}\\
		\guide{Instructor: Prof. Amit Sethi, IIT Bombay}
		\begin{myitemize}
			\item Estimated depth of a scene, using Color Attenuation Prior \textbf{(CAP)} and Dark Channel Prior \textbf{(DCP)}.
			\item Using the estimated depth, \textbf{reconstructed a haze-free image} based on atmosphere degradation model.
		\end{myitemize}

		\item \textbf{House sale status classification}
		\hfill{\textit{(Jan'18 - Apr'18)}}\\
		\guide{Instructor: Prof. Amit Sethi, IIT Bombay}
		\begin{myitemize}
			\item Based on the input attributes, \textbf{classified} house sale status.
			\item Used Random Forest, Support Vector Machine \textbf{(SVM)}, Perceptron, Gaussian Naive Bayes Algorithm, and K-Nearest Neighbor Algorithm classification models.
			\item Grid Search and Cross validation were done, for a subset of hyper parameters for each model, to increase cross validation accuracy.
		\end{myitemize}

		\item \textbf{Implementation of DBSCAN Algorithm from scratch}
		\hfill{\textit{(Jan'18 - Apr'18)}}\\
		\guide{Instructor: Prof. Amit Sethi, IIT Bombay}
		\begin{myitemize}
			\item \textbf{Developed} a program in python which will take a CSV as input and give labels of each data point as output, depending on the hyperparameters that are set.
			\item Utilized the implementation as a backend process for a web-based GUI, which \textbf{clusters} data points and \textbf{labels} them, each cluster having a different color.
		\end{myitemize}
	\end{myitemize}

	\highlight{TECHNICAL SKILLS}
	\begin{tabular}{m{1in}m{0.20in}m{4.5in}}
		\\[-3mm]
		\textbf{Languages} &: & {{C, C++, Bash Scripting, HTML, Javascript, jQuery, PHP, Python}} \\
		\\[-3.5mm]
		\textbf{Tools} &: & {Matlab, GNU Radio, \LaTeX, Git, Wireshark}\\
		\\[-4mm]
	\end{tabular}

	\highlight{RELEVANT COURSES}\\[0.2cm]
	\begin{tabular}{ l l l }
		\textbullet\ Digital Message Transmission &  \textbullet\ DSP and its Applications & \textbullet\ Introduction to Machine Learning\vspace{0.04cm}\\
		\textbullet\ Wireless and Mobile Communications & \textbullet\ Image Processing & \textbullet\ Applied Linear Algebra\vspace{0.04cm}\\
		\textbullet\ Information Theory and Coding & \textbullet\ Network Security  & \textbullet\ Communication Networks\\
	\end{tabular}
	\setlength{\tabcolsep}{0.2cm}
	\vspace{0.15cm}

	\highlight{POSITIONS OF RESPONSIBILITY}
	\begin{myitemize}
		\item \textbf {Web Secretary} \textpipe\ \mystyle{Hostel 1, IIT Bombay}
		\hfill{(\textit{Jul'17 - Jun'18})}
		\begin{myitemize}
			\item Development and Maintenance of Hostel 1 Web site, and Computers.
		\end{myitemize}
		
		\item \textbf{PG Bridge Course Overall Coordinator} \textpipe\ \mystyle{Electrical Department, IIT Bombay}
		\hfill{(\textit{Jul'18})}
		\begin{myitemize}
			\item Organized a week long program including hands-on workshops, and lectures for PG freshers.
			\item Executed the program effectively for more than \textbf{150} students, with a team of \textbf{20} volunteers.
		\end{myitemize}

		\item \textbf{Student Companion} \textpipe\ \mystyle{Institute Student Companion Program, IIT Bombay}
		\hfill{(\textit{Jul'18 - Jun'19})}
		\begin{myitemize}
			\item \textbf{Mentored} 7 M.Tech students by providing continuous help and support throughout the year.
			\item Played a key role in Department orientation, which included course registrations, 
			informal sessions and lab visits for PG freshers in \textit{Communication Engineering} specialization.
		\end{myitemize}

		

		\item \textbf{Web Nominee} \textpipe\ \mystyle{Post Graduate Academic Council, IIT Bombay}
		\hfill{(\textit{Jul'18 - Jun'19})}

		\item \textbf{Web Coordinator} \textpipe\ \mystyle{Students' Reading Group, Electrical Department, IIT Bombay} \hfill{(\textit{Jul'18 - Jun'19})}
	\end{myitemize}

	\highlight{OTHER ACTIVITIES \& INTERESTS}
	\begin{myitemize}
		\item \textbf{Volunteered} for \textbf{Python} workshop by PGAC, IIT Bombay \hfill{(\textit{Oct'18})}
		\item \textbf{Volunteered} for \textbf{Linux} workshop for Electrical Department PG Bridgecourse, IIT Bombay \hfill{(\textit{Jul'19})}
		\item \textbf{Hobbies}: Watching TV series, solving puzzles, chess, snooker
	\end{myitemize}

\end{document}
